Modelling at-bats in baseball using the generalised Pareto distribution

### 2023-02-21 bibat/examples/baseball/docs/report.qmd
Update docs

---
title: "Modelling at-bats in baseball using the generalised Pareto distribution"
subtitle: "A report created using bibat version 0.0.7"
author: "Teddy Groves"
bibliography: bibliography.bib
reference-location: margin
format:
  html: default
  pdf: default
filters:
  - include-code-files
---

@@

```{sh}
$ pip install bibat
```

@@

```{sh}
bibat
```

@@

```{sh}
baseball
├── CODE_OF_CONDUCT.md
├── LICENSE
├── Makefile
├── README.md
├── bibat_version.txt
├── data
│   └── raw
│       ├── raw_measurements.csv
│       └── readme.md
├── docs
│   ├── bibliography.bib
│   ├── img
│   │   ├── example.png
│   │   └── readme.md
│   └── report.qmd
├── inferences
│   ├── fake_interaction
│   │   └── config.toml
│   ├── interaction
│   │   └── config.toml
│   └── no_interaction
│       └── config.toml
├── investigate.ipynb
├── plots
│   ├── posterior_ll_comparison.png
│   └── posterior_predictive_comparison.png
├── prepare_data.py
├── pyproject.toml
├── requirements-tooling.txt
├── requirements.txt
├── sample.py
├── src
│   ├── __init__.py
│   ├── data_preparation_functions.py
│   ├── inference_configuration.py
│   ├── prepared_data.py
│   ├── readme.md
│   ├── stan
│   │   ├── custom_functions.stan
│   │   ├── multilevel-linear-regression.stan
│   │   └── readme.md
│   ├── stan_input_functions.py
│   └── util.py
└── tests
    ├── test_integration
    │   └── test_data_preparation.py
    └── test_unit
        ├── test_inference_configuration.py
        └── test_util.py
```

@@

```{sh}
$ cd baseball
$ make analysis
```

@@

```{sh}
$ source .venv/bin/activate
$ python fetch_data.py
```

@@

```{Makefile}
RAW_DATA = data/raw/2006.csv data/raw/bdb-main.csv data/raw/bdb-post.csv data/raw/bdb-apps.csv
...
$(RAW_DATA): $(ACTIVATE_VENV) && python fetch_data.py
```

@@

```{sh}
$ rm data/raw/raw_measurements.csv
```

@@

```{python}
from typing import Optional
import pandera as pa

@@

```{sh}
.
├── gpareto2006
│   └── config.toml
└── normal2006
    └── config.toml
```

@@

```{sh}
inferences
├── gpareto2006
│   ├── config.toml
│   └── idata.json
└── normal2006
    ├── config.toml
    └── idata.json
```

@@

The trickiest thing about my analysis was setting prior distributions for the
parameters $k$ and $\sigma$ in the generalised Pareto models. To choose some
more or less plausible values I did a few prior-mode model runs and checked the
distributions of the resulting `alpha` variables. I wanted to make sure that
they all lay in the range corresponding to batting averages between about 0.15
and a little over 0.4. Here is a graph that shows the 1% to 99% prior quantiles
for each player's latent success percentage in the 2006 dataset alongside their
actually realised success rate.

![](img/prior_quantiles.png)

@@

![](img/posterior_quantiles.png)

>>>>

---
title: "Modelling at-bats in baseball using the generalised Pareto distribution"
subtitle: "A report created using bibat version 0.0.12"
author: "Teddy Groves"
bibliography: bibliography.bib
reference-location: margin
toc: true
format:
  html:
    embed-resources: true
filters:
  - include-code-files
---

@@

```zsh
$ pip install bibat
```

@@

```zsh
bibat
```

@@

```zsh
baseball
├── CODE_OF_CONDUCT.md
├── LICENSE
├── Makefile
├── README.md
├── bibat_version.txt
├── data
│   └── raw
│       ├── raw_measurements.csv
│       └── readme.md
├── docs
│   ├── bibliography.bib
│   ├── img
│   │   ├── example.png
│   │   └── readme.md
│   └── report.qmd
├── inferences
│   ├── fake_interaction
│   │   └── config.toml
│   ├── interaction
│   │   └── config.toml
│   └── no_interaction
│       └── config.toml
├── investigate.ipynb
├── plots
│   ├── posterior_ll_comparison.png
│   └── posterior_predictive_comparison.png
├── prepare_data.py
├── pyproject.toml
├── requirements-tooling.txt
├── requirements.txt
├── sample.py
├── src
│   ├── __init__.py
│   ├── data_preparation_functions.py
│   ├── inference_configuration.py
│   ├── prepared_data.py
│   ├── readme.md
│   ├── stan
│   │   ├── custom_functions.stan
│   │   ├── multilevel-linear-regression.stan
│   │   └── readme.md
│   ├── stan_input_functions.py
│   └── util.py
└── tests
    ├── test_integration
    │   └── test_data_preparation.py
    └── test_unit
        ├── test_inference_configuration.py
        └── test_util.py
```

@@

```zsh
$ cd baseball
$ make analysis
```

@@

```zsh
$ source .venv/bin/activate
$ python fetch_data.py
```

@@

```makefile
RAW_DATA = data/raw/2006.csv \
	data/raw/bdb-main.csv \
	data/raw/bdb-post.csv \
	data/raw/bdb-apps.csv

...
$(RAW_DATA):
	. $(ACTIVATE_VENV) && python fetch_data.py
```

@@

```zsh
$ rm data/raw/raw_measurements.csv
```

@@

```python
from typing import Optional
import pandera as pa

@@

```zsh
.
├── gpareto2006
│   └── config.toml
└── normal2006
    └── config.toml
```

@@

```zsh
inferences
├── gpareto2006
│   ├── config.toml
│   └── idata.json
└── normal2006
    ├── config.toml
    └── idata.json
```

@@

The trickiest thing about my analysis was setting prior distributions for the
parameters $k$ and $\sigma$ in the generalised Pareto models. To choose some
more or less plausible values I did a few prior-mode model runs and checked the
distributions of the resulting `alpha` variables. I wanted to make sure that
they all lay in the range corresponding to batting averages between about 0.1
and a little over 0.4. Here is a graph that shows the 1% to 99% prior quantiles
for each player's latent success percentage in both datasets alongside their
actually realised success rates.

![](../plots/prior_quantiles.png)

@@

![](../plots/posterior_quantiles.png)
